The Multi-Stencil Language

### 2016-05-28 ARTICLES/IJPP/article/article.tex
Updated "Time, mesh, data"

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfig}
\usepackage{caption}
\usepackage{cite}
\usepackage{filecontents}
\usepackage{listings}
\usepackage{mathtools, cuted}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usetikzlibrary{calc,arrows,shapes,automata,petri,positioning,decorations.markings,shadows}

@@

%\newtheorem{theorem}{Theorem}[section]
\newtheorem{myprop}[theorem]{Proposition}
% \newenvironment{proof}[1][Proof]{\begin{trivlist}
% \item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{mydef}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{myth}[1][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

@@

%------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}
Contributions :
\begin{itemize}
\item Formalism of a multi-stencil program and its parallelization
\item The Multi-stencil Language: agnostic from the type of mesh and of the choosen implementation
\item A first implementation of the MSL compiler (static scheduling + fusion + dump to SkelGIS/components)
\item Evaluation of the different types of parallelism introduced + compiler + fusion
\end{itemize}
%------------------------------------------------------------------------------
\section{Related work}
\label{sect:rel}
\input{related.tex}
%------------------------------------------------------------------------------
\section{Computational model of Multi-Stencil Programs}
\label{sect:formalism}
\input{formalism.tex}
%------------------------------------------------------------------------------
\section{The Multi-Stencil Language}
\label{sect:msl}
\input{msl.tex}
%------------------------------------------------------------------------------
\section{Parallelization of Multi-Stencil Programs}
\label{sect:parallelism}
\input{parallelism.tex}
%------------------------------------------------------------------------------
\section{Static Scheduling and performance model}
\label{sect:msp}
\input{msp.tex}
%------------------------------------------------------------------------------
\section{Implementation}
\label{sect:comp}
\input{compiler.tex}
%------------------------------------------------------------------------------
\section{Evaluation}
\label{sect:eval}
\input{evaluation.tex}
%------------------------------------------------------------------------------
\section{Conclusion}
\label{sect:concl}
%------------------------------------------------------------------------------

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb, stmaryrd}
\usepackage{subfig}
\usepackage{caption}
\usepackage{cite}
\usepackage{enumitem}
\usepackage{filecontents}
\usepackage{listings}
\usepackage{mathtools, cuted}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usetikzlibrary{calc,arrows,shapes,automata,petri,positioning,decorations.markings,shadows}

@@

%\newtheorem{theorem}{Theorem}[section]
\newtheorem{myprop}[theorem]{Proposition}
% \newenvironment{proof}[1][Proof]{\begin{trivlist}
% \item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{mydef}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{myth}[1][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{mydefs}[1][Definitions]{\par\medskip\noindent\textbf{#1}\nopagebreak\begin{itemize}[noitemsep,topsep=.25\topsep]}{\end{itemize}}

@@

%------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}
Contributions :
\begin{itemize}
\item Formalism of a multi-stencil program and its parallelization
\item The Multi-stencil Language: agnostic from the type of mesh and of the choosen implementation
\item A first implementation of the MSL compiler (static scheduling + fusion + dump to SkelGIS/components)
\item Evaluation of the different types of parallelism introduced + compiler + fusion
\end{itemize}
%------------------------------------------------------------------------------
\section{Computational model of Multi-Stencil Programs}
\label{sect:formalism}
\input{formalism.tex}
%------------------------------------------------------------------------------
\section{The Multi-Stencil Language}
\label{sect:msl}
\input{msl.tex}
%------------------------------------------------------------------------------
\section{Parallelization of Multi-Stencil Programs}
\label{sect:parallelism}
\input{parallelism.tex}
%------------------------------------------------------------------------------
\section{Static Scheduling and performance model}
\label{sect:msp}
\input{msp.tex}
%------------------------------------------------------------------------------
\section{Implementation}
\label{sect:comp}
\input{compiler.tex}
%------------------------------------------------------------------------------
\section{Evaluation}
\label{sect:eval}
\input{evaluation.tex}
%------------------------------------------------------------------------------
\section{Related work}
\label{sect:rel}
\begin{itemize}
\item stencil compilers cartesian : Pochoir, PATUS for optimizations/parallelization of a single stencil kernel
\item stencil compilers unstructured meshes : Lizst for optimizations/parallelization of a single stencil kernel
\item Halide and Nabla for pipeline of stencil computations in image (Cartesian) = mesh dependent
\item Reuse of external solutions as SkelGIS, GA, Lizst, Pochoir etc.
\end{itemize}
%------------------------------------------------------------------------------
\section{Conclusion}
\label{sect:concl}
%------------------------------------------------------------------------------
